---
title: "child_doc.Rmd"
output: html_document
---

```{r packages3}
require(dplyr)
require(magrittr)
require(plotly)
require(tidyr)
require(reshape2)
require(ggplot2)
require(V.PhyloMaker)
require(phytools)
```

Authors can break long manuscripts into more manageable pieces by placing each chapter or section in their own Markdown file and using the R Markdown `child` option. Though most of the text (and code) in this document is contained in the file `computed_manuscript.Rmd`, the text for this section comes from `child_doc.Rmd`. Citations that are created in the child automatically get inserted into the final document, making it possible to create a single, unified bibliography. For instance, here's a reference for the [R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/).[@xieMarkdownCookbook2020].

```{r hipsometria}
ggplot(inv.paisagens.filtered, aes(DBH, Htot)) +                                # gráfico da hipsometria dos dados do paper
  geom_point(alpha = 0.1) + 
  theme_bw() + theme(panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(),
                     panel.background = element_blank(),
                     axis.line = element_line(colour = "black"))
```

```{r}
incrementosModel = glm(data = incremento, incAnual ~ minDBH, family=Gamma(link="log"))
summary(incrementosModel)
```

## Grupo ecológicos

```{r}
grupo = "Intermediate"
grupo = "Shade-tolerant"
grupo = "Light-demanding" 
grupo = "Pioneer"
grupo = "Emergent"

grupoEcologico = inv.paisagens.filtered %>%
  filter(GrupoEco == grupo)
```

```{r}
filogenia = grupoEcologico %>%                                                    # filogenia das spécies estudadas
  group_by(scientific.name, genera.name, family.name) %>%
  summarise(n = n()) %>%
  drop_na(family.name) %>%
  filter(!is.na(family.name)) %>%
  filter(family.name != 'NI')
```

```{r}
phy = phylo.maker(filogenia[,1:3])
tree = phy$scenario.3
plotTree(tree, type='fan', fsize=0.5, lwd=1, ftype='i')
```

```{r}
arvHaEspecie = inv.paisagens.filtered %>%
  filter(DBH >= 10) %>%
  group_by(area, plot, subplot, year, GrupoEco) %>% 
  summarise(ntree = sum(eqTree)) %>%
  drop_na(ntree) %>%
  group_by(area, plot, subplot, GrupoEco) %>%
  summarise(ntree = mean(ntree)) %>%
  group_by(area, GrupoEco) %>%
  summarise(ntree = sum(ntree)) %>%
  left_join(parcelasArea) %>%
  mutate(arvha = ntree / nplots) %>%
  group_by(GrupoEco) %>%
  summarise(arvha = mean(arvha))
```

```{r}
for(i in unique(inv.paisagens.filtered$GrupoEco)){
  numeroArvores = inv.paisagens.filtered %>%
    filter(GrupoEco == i) %>%
    filter(DBH >= 10) %>%
    group_by(area, plot, subplot, year, cc) %>% 
    summarise(ntree = sum(eqTree))  %>%
    drop_na(ntree) %>%
    group_by(area, cc) %>%
    summarise(narv = sum(ntree)) %>%
    left_join(parcelasArea) %>%
    mutate(arvha = narv / nplots) %>%
    group_by(cc) %>%
    summarise(arvha = mean(arvha))
  
  ggplot(numeroArvores, aes(cc, arvha)) + geom_col() +
    xlab('Diameter distribution') + ylab('Trees per hectare') +
    ggtitle(paste0(i)) + 
    theme_bw() + theme(panel.grid.major = element_blank(),
                       panel.grid.minor = element_blank(),
                       panel.background = element_blank(),
                       axis.line = element_line(colour = "black"))
}
```

```{r}
incremento = inv.paisagens %>%
  group_by(area, plot, subplot, tree, scientific.name, GrupoEco) %>%
  summarise(cc = min(cc), minDBH = min(DBH), maxDBH = max(DBH), 
            inc = max(DBH) - min(DBH), intervMed = max(year) - min(year), 
            incAnual = inc / intervMed) %>%
  filter(inc > 0) %>%
  drop_na(GrupoEco)
```

```{r}
incrementoGrupo = incremento %>%
  group_by(GrupoEco) %>%
  summarise(incDesv = sd(incAnual, na.rm = TRUE), incAnual = mean(incAnual), tp = 50 / incAnual)
```

```{r}
incremento$GrupoEco <- factor(incremento$GrupoEco, 
                              levels=c("OUTROS","Pioneer","Light-demanding", 
                                       "Intermediate", "Shade-tolerant", "Emergent"))
grupoEcoModel = glm(data = incremento, incAnual ~ minDBH + GrupoEco, family=Gamma(link="log"))
summary(grupoEcoModel)
```

## Comercial

```{r}
grupo = 0
grupo = 1

## Grupo Ecológico -------------------------------------------------------------
comercial = inv.paisagens.filtered %>%
  filter(comercial == grupo)
```

```{r}
filogenia = comercial %>%                                                    # filogenia das spécies estudadas
  group_by(scientific.name, genera.name, family.name) %>%
  summarise(n = n()) %>%
  drop_na(family.name) %>%
  filter(!is.na(family.name)) %>%
  filter(family.name != 'NI')
```

```{r}
phy = phylo.maker(filogenia[,1:3])
tree = phy$scenario.3
plotTree(tree, type='fan', fsize=0.5, lwd=1, ftype='i')
```

```{r}
arvHaEspecie = inv.paisagens.filtered %>%
  filter(DBH >= 10) %>%
  group_by(area, plot, subplot, year, comercial) %>% 
  summarise(ntree = sum(eqTree)) %>%
  drop_na(ntree) %>%
  group_by(area, plot, subplot, comercial) %>%
  summarise(ntree = mean(ntree)) %>%
  group_by(area, comercial) %>%
  summarise(ntree = sum(ntree)) %>%
  left_join(parcelasArea) %>%
  mutate(arvha = ntree / nplots) %>%
  group_by(comercial) %>%
  summarise(arvha = mean(arvha))
```

```{r}
for(i in c(0, 1)){
  numeroArvores = inv.paisagens.filtered %>%
    filter(comercial == i) %>%
    filter(DBH >= 10) %>%
    group_by(area, plot, subplot, year, cc) %>% 
    summarise(ntree = sum(eqTree))  %>%
    drop_na(ntree) %>%
    group_by(area, cc) %>%
    summarise(narv = sum(ntree)) %>%
    left_join(parcelasArea) %>%
    mutate(arvha = narv / nplots) %>%
    group_by(cc) %>%
    summarise(arvha = mean(arvha))
  
  ggplot(numeroArvores, aes(cc, arvha)) + geom_col() +
    xlab('Diameter distribution') + ylab('Trees per hectare') +
    ggtitle(paste0(i)) + 
    theme_bw() + theme(panel.grid.major = element_blank(),
                       panel.grid.minor = element_blank(),
                       panel.background = element_blank(),
                       axis.line = element_line(colour = "black"))
}
```

```{r}
incremento = inv.paisagens %>%
  group_by(area, plot, subplot, tree, scientific.name, comercial) %>%
  summarise(cc = min(cc), minDBH = min(DBH), maxDBH = max(DBH), 
            inc = max(DBH) - min(DBH), intervMed = max(year) - min(year), 
            incAnual = inc / intervMed) %>%
  filter(inc > 0)
```

```{r}
incrementoGrupo = incremento %>%
  group_by(comercial) %>%
  summarise(incDesv = sd(incAnual, na.rm = TRUE), incAnual = mean(incAnual), tp = 50 / incAnual)
```

```{r}
comercialModel = glm(data = incremento, incAnual ~ minDBH + comercial, family=Gamma(link="log"))
summary(comercialModel)
```


## Espécies

```{r}
filogenia = inv.paisagens.filtered %>%                                          # filogenia das spécies estudadas
  filter(comercial == 1) %>%
  group_by(scientific.name, genera.name, family.name) %>%
  summarise(n = n()) %>%
  drop_na(family.name) %>%
  filter(!is.na(family.name)) %>%
  filter(family.name != 'NI')
```

```{r}
phy = phylo.maker(filogenia[,1:3])
#write.tree(phy$scenario.3, "Figure.1.tre")
tree = phy$scenario.3
plotTree(tree, type='fan', fsize=0.5, lwd=3, ftype='i')

```

```{r}
speciesList = inv.paisagens.filtered %>%                                        # Lista das espécies com maior número de árvores
  filter(comercial == 1) %>%                                                    # filtra espécies comerciais
  group_by(scientific.name) %>%
  summarise(ntree = n()) %>%
  filter(ntree > 60) %>%
  select(scientific.name)
```

```{r}
arvHaEspecie = inv.paisagens.filtered %>%
  filter(DBH >= 10) %>%
  group_by(area, plot, subplot, year, scientific.name) %>% 
  summarise(ntree = sum(eqTree)) %>%
  drop_na(ntree) %>%
  group_by(area, plot, subplot, scientific.name) %>%
  summarise(ntree = mean(ntree)) %>%
  group_by(area, scientific.name) %>%
  summarise(ntree = sum(ntree)) %>%
  left_join(parcelasArea) %>%
  mutate(arvha = ntree / nplots) %>%
  group_by(scientific.name) %>%
  summarise(arvha = mean(arvha)) %>%
  filter(scientific.name %in% speciesList$scientific.name)
```


```{r eval=FALSE}
for(i in speciesList$scientific.name){
  numeroArvores = inv.paisagens.filtered %>%
    filter(scientific.name == i) %>%
    filter(DBH >= 10) %>%
    group_by(area, plot, subplot, year, cc) %>% 
    summarise(ntree = sum(eqTree))  %>%
    drop_na(ntree) %>%
    group_by(area, cc) %>%
    summarise(narv = sum(ntree)) %>%
    left_join(parcelasArea) %>%
    mutate(arvha = narv / nplots) %>%
    group_by(cc) %>%
    summarise(arvha = mean(arvha))
    
  ggplot(numeroArvores, aes(cc, arvha)) + geom_col() +
    xlab('Diameter distribution') + ylab('Trees per hectare') +
    ggtitle(paste0(i)) + 
    theme_bw() + theme(panel.grid.major = element_blank(),
                       panel.grid.minor = element_blank(),
                       panel.background = element_blank(),
                       axis.line = element_line(colour = "black"))
}
```


```{r}
incremento = inv.paisagens %>%
  group_by(area, plot, subplot, tree, scientific.name) %>%
  summarise(cc = min(cc), minDBH = min(DBH), maxDBH = max(DBH), 
            inc = max(DBH) - min(DBH), intervMed = max(year) - min(year), 
            incAnual = inc / intervMed) %>%
  filter(inc > 0)
```


```{r}
incrementoSpecies = incremento %>%
  filter(scientific.name %in% speciesList$scientific.name) %>%
  group_by(scientific.name) %>%
  summarise(incAnual = mean(incAnual), tp = 50 / incAnual)
```

```{r}
ggplot(incremento, aes(as.factor(cc), incAnual)) + geom_boxplot() +
  xlab('Diameter class') +
  theme_bw() + theme(panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(),
                     panel.background = element_blank(),
                     axis.line = element_line(colour = "black"))
```



